---
title: "04201052"
format: html
editor: visual
---

# Intro

We saw in the previous file that when we perform vanilla SINDy in all cells, the picture is not clear. The coefficients and p-values are all over the place. And the regression is seriously under determined in a lot of the cases. So we restrict here to the cells for which the regression is succesful.  

# Methods

For each cell, we perform the SINDy regression. We then keep the results of only those for which $R^2 > 0.2$. 

```{r}
#| include: false
data <- t(read.csv("10G.csv", header=FALSE))

coeffs1 <- vector()
pvals1 <- vector()
coeffs2 <- vector()
pvals2 <- vector()
rs.squared <- vector()
for(i in 1:11598){
  
  # Save data in variable 
  ex.data <- data[i, 1:40]
  
  # Differentiate and forget first entry
  d.ex.data <- diff(ex.data)[2:40]
  
  # Forget first entry of the data
  ex.data.cut <- data[i, 2:40]
  
  try(
    # Create linear model 
    {model <- lm( d.ex.data ~ poly(ex.data.cut, 3))
    if(summary(model)$r.squared > 0.2){
      coeffs1 <- c(coeffs1, model$coefficients['poly(ex.data.cut, 3)1'])
      coeffs2 <-c(coeffs2, model$coefficients['poly(ex.data.cut, 3)2'])
      pvals1 <- c(pvals1, summary(model)$coefficients['poly(ex.data.cut, 3)1', 'Pr(>|t|)'])
      pvals2 <- c(pvals2,summary(model)$coefficients['poly(ex.data.cut, 3)2', 'Pr(>|t|)'])
      rs.squared <- c(rs.squared, summary(model)$r.squared)
    }
    }
  )
}
```

# Results

## Linear Term

<!-- ```{r} -->
<!-- boxplot(pvals1) -->
<!-- ``` -->

```{r}
hist(pvals1)
```

```{r}
length(pvals1)
```

So the linear term is significant in about `r 100*(800/length(pvals1))` percent of the instances. 

Additionally,

```{r}
summary(coeffs1)
```

So we cannot tell definitely the sign of the linear term, though there is some indication that it should be negative. 


## Quadratic Term 

```{r}
hist(pvals2)
```


The quadratic term is significant about twice as frequently. 

```{r}
summary(coeffs2)
```

We can be pretty confident that the sign of the quadratic term is negative. Plus the median seems like a reasonable estimate for the coefficient. 

## Goodness of fit 

Of course, this is biased, but FWIW:

```{r}
hist(rs.squared)
```












